\textit{MSF: Modulated Sub-path Finder}

### 2018-01-16 MSF_Paper_FA.tex
changing path in includefig to make it pdflatex-ing
Update MSF_Paper_FA.tex

Likewise we compared gene enrichment results of sub-module genes identified by \texttt{MSF} using Reactome FI to the Reactome pathway enrichment analysis results. Although MSF and Reactome show good agreement on the dis-regulated pathways e.g Signaling by Interleukins, Interleukin-10 signaling, Cytokine Signaling in Immune system, Chemokine receptors bind chemokines, RIG-I/MDA5 mediated induction of IFN-alpha/beta pathways, NF-kB activation, Reactome as well fails to identify the Toll-like recpetor signaling. On the other hand, \texttt{MSF} could not identify the dis-regulation of phases of cell cycle. This shows that \texttt{MSF} is able to identify the modulated genes in the sub-modules at the earliest time-point of infection even though when the signal transduction was weak.

@@

To show the robustness and stability of our method, Poisson
distributed noise was added to the sample read counts. 
Then DGEA was carried out on the disturbed data with the
same parameters as for the native data, followed by analysis with
\texttt{MSF}. Using this criteria, the goal was to spot almost
identical modulated sub-paths in the real and noisy data.

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/Tgfb1} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep1}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep2} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Documents/PhDThesis/MSFPaper/TGFBstep3}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-paths. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-paths, sub-path1 found one with M,K,C and the second modulated sub-path2 S,V,T, (c) shows the modulated sub-path1 being extended to M,K,C,A,D, (d) shows both the modulated sub=paths merged with the addition of 3 genes Z,W,P.}
\end{figure*}

>>>>

Likewise we compared gene enrichment results of sub-module genes identified by \texttt{MSF} using Reactome FI to the Reactome pathway enrichment analysis results. Although MSF and Reactome show good agreement on the dis-regulated pathways e.g Signaling by Interleukins, Interleukin-10 signaling, Cytokine Signaling in Immune system, Chemokine receptors bind chemokines, RIG-I/MDA5 mediated induction of IFN-alpha/beta pathways, NF-kB activation, Reactome as well fails to identify the Toll-like receptor signaling. On the other hand, \texttt{MSF} could not identify the dis-regulation of phases of cell cycle. This shows that \texttt{MSF} is able to identify the modulated genes in the sub-modules at the earliest time-point of infection even though when the signal transduction was weak.

@@

To show the robustness and stability of our method, Poisson
distributed noise was added to the sample read counts. 
Then DGEA was carried out on the disturbed data with the
same parameters as for the native data, followed by analysis with
\texttt{MSF}. Using this criteria, the goal was to spot almost
identical modulated sub-paths in the real and noisy data. This procedure was carried out 100 times and every time the genes from the sub-modules identified from noisy data were compared to the sub-modules identified from the native data. The robustness of MSF for the three time-points is shown in~(Fig.~2). For the last time-point (2dpi) 84\% genes of the sub-modules from native data were retrieved, for 1dpi the robustness was about 79\%. The robustness was the lowest at 6hpi nearly 71\%, this could be due to that the infection merely started and the signal transdcution was weak as compared to the later time-points and over that Poisson distributed noise was added to the data.

@@

	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{Tgfb1.png} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep1.png}
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep2.png} 
		\caption{}
	\end{subfigure}
	\begin{subfigure}{.5\textwidth}
		\centering
		\includegraphics[width=10.0cm]{TGFBstep3.png}
		\caption{}
	\end{subfigure}
	\caption{Overview of \texttt{MSF} process showing the steps to identify the modulated sub-paths. (a) showing a network of genes with green nodes as genes with \textit{p}-values $< $ 0.05, and blue nodes are genes with \textit{p}-values $>$ 0.05, (b) the genes circled red show the two initial modulated sub-paths, sub-path1 found one with M,K,C and the second modulated sub-path2 S,V,T, (c) shows the modulated sub-path1 being extended to M,K,C,A,D, (d) shows both the modulated sub=paths merged with the addition of 3 genes Z,W,P.}
\end{figure*}
